dads manual

### 2021-01-12 inst/gitbook/_book/dads_manual.tex
Updated gitbook for version 0.1.3

\title{dads manual}
\author{Thomas Guillerme (\href{mailto:guillert@tcd.ie}{\nolinkurl{guillert@tcd.ie}}), Alex Slavenko (email) and others}
\date{2020-12-04}

@@

\CommentTok{## Installing the latest version directly from GitHub}
\KeywordTok{install_github}\NormalTok{(}\StringTok{"TGuillerme/dads"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
## $A
## $A$process
## function (x0, edge.length = 1, Sigma = diag(length(x0)), ...) 
## {
##     return(t(MASS::mvrnorm(n = 1, mu = x0, Sigma = Sigma * edge.length, 
##         ...)))
## }
## <bytecode: 0x7f7eeee57f58>
## <environment: namespace:dads>
## 
## $A$start
## [1] 0
## 
## $A$trait_id
## [1] 1
\end{verbatim}

@@

\CommentTok{## Setting some parameters for generating trees}
\NormalTok{bd_params  <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{extinction =} \DecValTok{0}\NormalTok{)}
\NormalTok{stope_rule <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{max.living =} \DecValTok{20}\NormalTok{)}

\CommentTok{## Generating a tree with the default branch length parameter}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{0}\NormalTok{)}
\NormalTok{default_tree <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd_params,}
                     \DataTypeTok{stop.rule =}\NormalTok{ stope_rule,}
                     \DataTypeTok{modifiers =}\NormalTok{ default_modifiers)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{## Generating a new tree with this modifier}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{0}\NormalTok{)}
\NormalTok{modified_tree <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd_params,}
                      \DataTypeTok{stop.rule =}\NormalTok{ stope_rule,}
                      \DataTypeTok{modifiers =}\NormalTok{ constant_modifier)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{## Generating a new tree with this modifier}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{0}\NormalTok{)}
\NormalTok{increasing_tree <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd_params,}
                        \DataTypeTok{stop.rule =}\NormalTok{ stope_rule,}
                        \DataTypeTok{modifiers =}\NormalTok{ increasing_modifier)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## A modifier for selection}
\NormalTok{ladderised_modifier <-}\StringTok{ }\KeywordTok{make.modifiers}\NormalTok{(}\DataTypeTok{selection =}\NormalTok{ select.last)}
\CommentTok{## Generating a new tree with this modifier}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{0}\NormalTok{)}
\NormalTok{ladderised_tree <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd_params,}
                        \DataTypeTok{stop.rule =}\NormalTok{ stope_rule,}
                        \DataTypeTok{modifiers =}\NormalTok{ ladderised_modifier)}
\CommentTok{## Displaying the results}
\KeywordTok{par}\NormalTok{(}\DataTypeTok{mfrow =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{2}\NormalTok{))}
\KeywordTok{plot}\NormalTok{(default_tree,    }\DataTypeTok{main =} \StringTok{"Default modifier"}\NormalTok{)}
\KeywordTok{plot}\NormalTok{(ladderised_tree, }\DataTypeTok{main =} \StringTok{"Ladderising modifier"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{## Simulate a tree and trait with no modifier}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{1}\NormalTok{)}
\NormalTok{default_dads <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd_params,}
                     \DataTypeTok{stop.rule =}\NormalTok{ stope_rule,}
                     \DataTypeTok{traits    =}\NormalTok{ BM_trait)}

\CommentTok{## Simulate a tree and trait with the modifier}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{1}\NormalTok{)}
\NormalTok{skewed_trait_dads <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd_params,}
                          \DataTypeTok{stop.rule =}\NormalTok{ stope_rule,}
                          \DataTypeTok{traits    =}\NormalTok{ BM_trait,}
                          \DataTypeTok{modifiers =}\NormalTok{ positive_skew)}

@@

\CommentTok{## Generating a new tree with this modifier}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{0}\NormalTok{)}
\NormalTok{modified_tree <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd_params,}
                      \DataTypeTok{stop.rule =}\NormalTok{ stope_rule,}
                      \DataTypeTok{modifiers =}\NormalTok{ random_extinction)}

@@

\CommentTok{## Simulate a tree and trait with the modifier}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{1}\NormalTok{)}
\NormalTok{biased_trait_dads <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd_params,}
                          \DataTypeTok{stop.rule =}\NormalTok{ stope_rule,}
                          \DataTypeTok{traits    =}\NormalTok{ BM_trait,}
                          \DataTypeTok{modifiers =}\NormalTok{ biased_trait)}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{bd.params <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{speciation =} \DecValTok{1}\NormalTok{, }\DataTypeTok{extinction =} \DecValTok{1}\OperatorTok{/}\DecValTok{3}\NormalTok{)}
\NormalTok{traits <-}\StringTok{ }\KeywordTok{make.traits}\NormalTok{()}
\NormalTok{stop.rule <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{max.taxa =} \DecValTok{20}\NormalTok{, }\DataTypeTok{max.living =} \OtherTok{Inf}\NormalTok{, }\DataTypeTok{max.time =} \OtherTok{Inf}\NormalTok{)}
\NormalTok{modifiers <-}\StringTok{ }\OtherTok{NULL}
\NormalTok{events <-}\StringTok{ }\OtherTok{NULL}
\NormalTok{null.error <-}\StringTok{ }\OtherTok{NULL}

\CommentTok{## modifiers}
\NormalTok{condition <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(trait.values, parent.lineage) }\KeywordTok{return}\NormalTok{(}\KeywordTok{parent.traits}\NormalTok{(trait.values, parent.lineage) }\OperatorTok{<}\StringTok{ }\DecValTok{0}\NormalTok{)}
\NormalTok{modify <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(x) }\KeywordTok{return}\NormalTok{(x }\OperatorTok{*}\StringTok{ }\DecValTok{20}\NormalTok{)}

\CommentTok{## Setting up the different modifiers}
\NormalTok{modify_speciation <-}\StringTok{ }\KeywordTok{make.modifiers}\NormalTok{(}\DataTypeTok{speciation    =}\NormalTok{ speciation.trait,}
                                    \DataTypeTok{condition     =}\NormalTok{ condition,}
                                    \DataTypeTok{modify        =}\NormalTok{ modify)}
\NormalTok{modify_brlen <-}\StringTok{ }\KeywordTok{make.modifiers}\NormalTok{(}\DataTypeTok{branch.length =}\NormalTok{ branch.length.trait,}
                               \DataTypeTok{condition     =}\NormalTok{ condition,}
                               \DataTypeTok{modify        =}\NormalTok{ modify)}
\NormalTok{modify_speciation_brlen <-}\StringTok{ }\KeywordTok{make.modifiers}\NormalTok{(}\DataTypeTok{branch.length =}\NormalTok{ branch.length.trait,}
                                          \DataTypeTok{speciation    =}\NormalTok{ speciation.trait,}
                                          \DataTypeTok{condition     =}\NormalTok{ condition,}
                                          \DataTypeTok{modify        =}\NormalTok{ modify)}

\CommentTok{## Test normal (no modifiers)}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{1}\NormalTok{)}
\NormalTok{test <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(bd.params, stop.rule, traits, }\DataTypeTok{null.error =} \DecValTok{20}\NormalTok{)}
\KeywordTok{par}\NormalTok{(}\DataTypeTok{mfrow =} \KeywordTok{c}\NormalTok{(}\DecValTok{4}\NormalTok{,}\DecValTok{2}\NormalTok{))}
\KeywordTok{plot}\NormalTok{(test}\OperatorTok{$}\NormalTok{tree)}
\KeywordTok{plot.dads}\NormalTok{(test, }\DataTypeTok{main =} \StringTok{"random tree + trait"}\NormalTok{)}

\CommentTok{## Test with modifiers}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{1}\NormalTok{)}
\NormalTok{trait_table <-}\StringTok{ }\OtherTok{NULL}
\NormalTok{test <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(bd.params, stop.rule, traits,}
                                \DataTypeTok{modifiers =}\NormalTok{ modify_speciation,}
                                \DataTypeTok{null.error =} \DecValTok{20}\NormalTok{)}
\KeywordTok{plot}\NormalTok{(test}\OperatorTok{$}\NormalTok{tree)}
\KeywordTok{plot.dads}\NormalTok{(test, }\DataTypeTok{main =} \StringTok{"Skewed speciation"}\NormalTok{)}

\KeywordTok{set.seed}\NormalTok{(}\DecValTok{1}\NormalTok{)}
\NormalTok{trait_table <-}\StringTok{ }\OtherTok{NULL}
\NormalTok{test <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(bd.params, stop.rule, traits,}
                                \DataTypeTok{modifiers =}\NormalTok{ modify_brlen,}
                                \DataTypeTok{null.error =} \DecValTok{20}\NormalTok{)}
\KeywordTok{plot}\NormalTok{(test}\OperatorTok{$}\NormalTok{tree)}
\KeywordTok{plot.dads}\NormalTok{(test, }\DataTypeTok{main =} \StringTok{"Skewed branch length"}\NormalTok{)}

\KeywordTok{set.seed}\NormalTok{(}\DecValTok{1}\NormalTok{)}
\NormalTok{trait_table <-}\StringTok{ }\OtherTok{NULL}
\NormalTok{test <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(bd.params, stop.rule, traits,}
                                \DataTypeTok{modifiers =}\NormalTok{ modify_speciation_brlen,}
                                \DataTypeTok{null.error =} \DecValTok{20}\NormalTok{)}
\KeywordTok{plot}\NormalTok{(test}\OperatorTok{$}\NormalTok{tree)}
\KeywordTok{plot.dads}\NormalTok{(test, }\DataTypeTok{main =} \StringTok{"Skewed branch length and speciation"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

>>>>

\title{dads manual}
\author{Thomas Guillerme (\href{mailto:guillert@tcd.ie}{\nolinkurl{guillert@tcd.ie}}), Alex Slavenko (email) and others}
\date{2021-01-12}

@@

\CommentTok{## Installing the latest version directly from GitHub}
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"TGuillerme/dads"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
## $A
## $A$process
## function (x0, edge.length = 1, Sigma = diag(length(x0)), ...) 
## {
##     return(t(MASS::mvrnorm(n = 1, mu = x0, Sigma = Sigma * edge.length, 
##         ...)))
## }
## <bytecode: 0x7faff6222240>
## <environment: namespace:dads>
## 
## $A$start
## [1] 0
## 
## $A$trait_id
## [1] 1
\end{verbatim}

@@

\CommentTok{## Setting some parameters for generating trees}
\NormalTok{bd_params <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{extinction =} \DecValTok{0}\NormalTok{)}
\NormalTok{stop_rule <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{max.living =} \DecValTok{20}\NormalTok{)}

\CommentTok{## Generating a tree with the default branch length parameter}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{0}\NormalTok{)}
\NormalTok{default_tree <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd_params,}
                     \DataTypeTok{stop.rule =}\NormalTok{ stop_rule,}
                     \DataTypeTok{modifiers =}\NormalTok{ default_modifiers)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{## Generating a new tree with this modifier}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{0}\NormalTok{)}
\NormalTok{modified_tree <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd_params,}
                      \DataTypeTok{stop.rule =}\NormalTok{ stop_rule,}
                      \DataTypeTok{modifiers =}\NormalTok{ constant_modifier)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{## Generating a new tree with this modifier}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{0}\NormalTok{)}
\NormalTok{increasing_tree <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd_params,}
                        \DataTypeTok{stop.rule =}\NormalTok{ stop_rule,}
                        \DataTypeTok{modifiers =}\NormalTok{ increasing_modifier)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## A modifier for selection}
\NormalTok{ladderised_modifier <-}\StringTok{ }\KeywordTok{make.modifiers}\NormalTok{(}\DataTypeTok{selection =}\NormalTok{ select.last)}
\CommentTok{## Generating a new tree with this modifier}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{0}\NormalTok{)}
\NormalTok{ladderised_tree <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd_params,}
                        \DataTypeTok{stop.rule =}\NormalTok{ stop_rule,}
                        \DataTypeTok{modifiers =}\NormalTok{ ladderised_modifier)}
\CommentTok{## Displaying the results}
\KeywordTok{par}\NormalTok{(}\DataTypeTok{mfrow =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{2}\NormalTok{))}
\KeywordTok{plot}\NormalTok{(default_tree,    }\DataTypeTok{main =} \StringTok{"Default modifier"}\NormalTok{)}
\KeywordTok{plot}\NormalTok{(ladderised_tree, }\DataTypeTok{main =} \StringTok{"Ladderising modifier"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{## Simulate a tree and trait with no modifier}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{1}\NormalTok{)}
\NormalTok{default_dads <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd_params,}
                     \DataTypeTok{stop.rule =}\NormalTok{ stop_rule,}
                     \DataTypeTok{traits    =}\NormalTok{ BM_trait)}

\CommentTok{## Simulate a tree and trait with the modifier}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{1}\NormalTok{)}
\NormalTok{skewed_trait_dads <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd_params,}
                          \DataTypeTok{stop.rule =}\NormalTok{ stop_rule,}
                          \DataTypeTok{traits    =}\NormalTok{ BM_trait,}
                          \DataTypeTok{modifiers =}\NormalTok{ positive_skew)}

@@

\CommentTok{## Generating a new tree with this modifier}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{0}\NormalTok{)}
\NormalTok{modified_tree <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd_params,}
                      \DataTypeTok{stop.rule =}\NormalTok{ stop_rule,}
                      \DataTypeTok{modifiers =}\NormalTok{ random_extinction)}

@@

\CommentTok{## Simulate a tree and trait with the modifier}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{1}\NormalTok{)}
\NormalTok{biased_trait_dads <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd_params,}
                          \DataTypeTok{stop.rule =}\NormalTok{ stop_rule,}
                          \DataTypeTok{traits    =}\NormalTok{ BM_trait,}
                          \DataTypeTok{modifiers =}\NormalTok{ biased_trait)}

@@

\hypertarget{makeevents}{%
\chapter{\texorpdfstring{Making events with \texttt{make.events()}}{Making events with make.events()}}\label{makeevents}}

\hypertarget{conditions}{%
\section{Conditions}\label{conditions}}

\hypertarget{modifications}{%
\section{Modifications}\label{modifications}}

\hypertarget{some-events-examples}{%
\section{Some events examples}\label{some-events-examples}}

\hypertarget{random-mass-extinction-after-some-time}{%
\subsection{Random mass extinction after some time}\label{random-mass-extinction-after-some-time}}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Simulation parameters}
\NormalTok{stop.rule <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{max.time =} \DecValTok{5}\NormalTok{)}
\NormalTok{bd.params <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{extinction =} \DecValTok{0}\NormalTok{, }\DataTypeTok{speciation =} \DecValTok{1}\NormalTok{)}

\CommentTok{## 80% mass extinction at time 4}
\NormalTok{mass_extinction <-}\StringTok{ }\KeywordTok{make.events}\NormalTok{(}
                      \DataTypeTok{target =} \StringTok{"taxa"}\NormalTok{,}
                      \DataTypeTok{condition =} \KeywordTok{time.condition}\NormalTok{(}\DecValTok{4}\NormalTok{),}
                      \DataTypeTok{modification =} \KeywordTok{random.extinction}\NormalTok{(}\FloatTok{0.8}\NormalTok{))}

\CommentTok{## Running the simulations}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{1}\NormalTok{)}
\NormalTok{results <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd.params,}
                \DataTypeTok{stop.rule =}\NormalTok{ stop.rule,}
                \DataTypeTok{events    =}\NormalTok{ mass_extinction)}
\CommentTok{## Plotting the results}
\KeywordTok{plot}\NormalTok{(results, }\DataTypeTok{show.tip.label =} \OtherTok{FALSE}\NormalTok{)}
\KeywordTok{axisPhylo}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{dads_manual_files/figure-latex/unnamed-chunk-57-1.pdf}

\hypertarget{extinction-based-on-a-trait-value-after-some-time}{%
\subsection{Extinction based on a trait value after some time}\label{extinction-based-on-a-trait-value-after-some-time}}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Simulation parameters}
\NormalTok{stop.rule <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{max.time =} \DecValTok{5}\NormalTok{)}
\NormalTok{bd.params <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{extinction =} \DecValTok{0}\NormalTok{, }\DataTypeTok{speciation =} \DecValTok{1}\NormalTok{)}

\CommentTok{## Extinction of any tips with trait < 1 at time 4}
\NormalTok{trait_extinction <-}\StringTok{ }\KeywordTok{make.events}\NormalTok{(}
                      \DataTypeTok{target =} \StringTok{"taxa"}\NormalTok{,}
                      \DataTypeTok{condition =} \KeywordTok{time.condition}\NormalTok{(}\DecValTok{4}\NormalTok{),}
                      \DataTypeTok{modification =} \KeywordTok{trait.extinction}\NormalTok{(}\DecValTok{1}\NormalTok{))}

\CommentTok{## Running the simulations}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{7}\NormalTok{)}
\NormalTok{results <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd.params,}
                \DataTypeTok{stop.rule =}\NormalTok{ stop.rule,}
                \DataTypeTok{traits    =} \KeywordTok{make.traits}\NormalTok{(),}
                \DataTypeTok{events    =}\NormalTok{ trait_extinction)}
\CommentTok{## Plotting the results}
\KeywordTok{plot}\NormalTok{(results)}
\end{Highlighting}
\end{Shaded}

\includegraphics{dads_manual_files/figure-latex/unnamed-chunk-58-1.pdf}

\hypertarget{adding-a-background-extinction-after-reaching-a-number-of-living-taxa}{%
\subsection{Adding a background extinction after reaching a number of living taxa}\label{adding-a-background-extinction-after-reaching-a-number-of-living-taxa}}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Simulation parameters}
\NormalTok{stop.rule <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{max.living =} \DecValTok{50}\NormalTok{)}
\NormalTok{bd.params <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{extinction =} \DecValTok{0}\NormalTok{, }\DataTypeTok{speciation =} \DecValTok{1}\NormalTok{)}

\CommentTok{## Adding an extinction parameter after 30 taxa}
\NormalTok{background_extinction <-}\StringTok{ }\KeywordTok{make.events}\NormalTok{(}
                      \DataTypeTok{condition    =} \KeywordTok{taxa.condition}\NormalTok{(}\DecValTok{30}\NormalTok{),}
                      \DataTypeTok{target       =} \StringTok{"bd.params"}\NormalTok{,}
                      \DataTypeTok{modification =} \KeywordTok{update.bd.params}\NormalTok{(}\DecValTok{1}\OperatorTok{/}\DecValTok{3}\NormalTok{, }\StringTok{"extinction"}\NormalTok{))}

\CommentTok{## Running the simulations}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{2}\NormalTok{)}
\NormalTok{results <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd.params,}
                \DataTypeTok{stop.rule =}\NormalTok{ stop.rule,}
                \DataTypeTok{events    =}\NormalTok{ background_extinction)}
\CommentTok{## Plotting the results}
\KeywordTok{plot}\NormalTok{(results)}
\end{Highlighting}
\end{Shaded}

\includegraphics{dads_manual_files/figure-latex/unnamed-chunk-59-1.pdf}

\hypertarget{reducing-speciation-after-some-time}{%
\subsection{Reducing speciation after some time}\label{reducing-speciation-after-some-time}}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Simulation parameters}
\NormalTok{stop.rule <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{max.time =} \DecValTok{4}\NormalTok{)}
\NormalTok{bd.params <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{extinction =} \DecValTok{0}\NormalTok{, }\DataTypeTok{speciation =} \DecValTok{1}\NormalTok{)}

\CommentTok{## Reducing speciation after reaching time 2}
\NormalTok{reduced_speciation <-}\StringTok{ }\KeywordTok{make.events}\NormalTok{(}
                      \DataTypeTok{condition    =} \KeywordTok{time.condition}\NormalTok{(}\DecValTok{2}\NormalTok{),}
                      \DataTypeTok{target       =} \StringTok{"bd.params"}\NormalTok{,}
                      \DataTypeTok{modification =} \KeywordTok{update.bd.params}\NormalTok{(}\DecValTok{1}\OperatorTok{/}\DecValTok{3}\NormalTok{, }\StringTok{"speciation"}\NormalTok{))}

\KeywordTok{set.seed}\NormalTok{(}\DecValTok{42}\NormalTok{)}
\NormalTok{no_event <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd.params,}
                 \DataTypeTok{stop.rule =}\NormalTok{ stop.rule)}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{42}\NormalTok{)}
\NormalTok{reduced_speciation_event <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd.params,}
                                 \DataTypeTok{stop.rule =}\NormalTok{ stop.rule,}
                                 \DataTypeTok{events    =}\NormalTok{ reduced_speciation)}

\CommentTok{## Plot both trees}
\KeywordTok{par}\NormalTok{(}\DataTypeTok{mfrow =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{))}
\KeywordTok{plot}\NormalTok{(no_event, }\DataTypeTok{main =} \StringTok{"No event"}\NormalTok{)}
\KeywordTok{axisPhylo}\NormalTok{()}
\KeywordTok{plot}\NormalTok{(reduced_speciation_event, }\DataTypeTok{main =} \StringTok{"Reduced speciation after time 2"}\NormalTok{)}
\KeywordTok{axisPhylo}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{dads_manual_files/figure-latex/unnamed-chunk-60-1.pdf}

\hypertarget{changing-trait-process-after-some-time}{%
\subsection{Changing trait process after some time}\label{changing-trait-process-after-some-time}}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Simulation parameters}
\NormalTok{bd.params <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{extinction =} \DecValTok{0}\NormalTok{, }\DataTypeTok{speciation =} \DecValTok{1}\NormalTok{)}
\NormalTok{stop.rule <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{max.time =} \DecValTok{6}\NormalTok{)}
\NormalTok{traits    <-}\StringTok{ }\KeywordTok{make.traits}\NormalTok{()}

\CommentTok{## Create an event to change the trait process}
\NormalTok{change_process <-}\StringTok{ }\KeywordTok{make.events}\NormalTok{(}
                  \DataTypeTok{condition    =} \KeywordTok{time.condition}\NormalTok{(}\DecValTok{5}\NormalTok{),}
                  \DataTypeTok{target       =} \StringTok{"traits"}\NormalTok{,}
                  \DataTypeTok{modification =} \KeywordTok{update.traits}\NormalTok{(}\DataTypeTok{process =}\NormalTok{ OU.process))}

\CommentTok{## Run the simulations}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{1}\NormalTok{)}
\NormalTok{no_change <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd.params,}
                  \DataTypeTok{stop.rule =}\NormalTok{ stop.rule,}
                  \DataTypeTok{traits    =}\NormalTok{ traits)}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{1}\NormalTok{)}
\NormalTok{process_change <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd.params,}
                       \DataTypeTok{stop.rule =}\NormalTok{ stop.rule,}
                       \DataTypeTok{traits    =}\NormalTok{ traits,}
                       \DataTypeTok{events    =}\NormalTok{ change_process)}
\CommentTok{## Plot the results}
\KeywordTok{par}\NormalTok{(}\DataTypeTok{mfrow =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{2}\NormalTok{))}
\KeywordTok{plot}\NormalTok{(no_change, }\DataTypeTok{ylim =} \KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{7}\NormalTok{, }\DecValTok{7}\NormalTok{))}
\KeywordTok{plot}\NormalTok{(process_change, }\DataTypeTok{ylim =} \KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{7}\NormalTok{, }\DecValTok{7}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{dads_manual_files/figure-latex/unnamed-chunk-61-1.pdf}

\hypertarget{changing-trait-correlation-after-reaching-a-trait-value}{%
\subsection{Changing trait correlation after reaching a trait value}\label{changing-trait-correlation-after-reaching-a-trait-value}}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Set the parameters}
\NormalTok{stop.rule <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{max.taxa =} \DecValTok{100}\NormalTok{)}
\NormalTok{bd.params <-}\StringTok{ }\KeywordTok{list}\NormalTok{(}\DataTypeTok{extinction =} \DecValTok{0}\NormalTok{, }\DataTypeTok{speciation =} \DecValTok{1}\NormalTok{)}

\CommentTok{## A correlated trait}
\NormalTok{traits <-}\StringTok{ }\KeywordTok{make.traits}\NormalTok{(}\DataTypeTok{n =} \DecValTok{2}\NormalTok{, }\DataTypeTok{process.args =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{Sigma =} \KeywordTok{matrix}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{, }\DecValTok{2}\NormalTok{)))}

\CommentTok{## Event changing a trait correlation}
\NormalTok{change_correlation <-}\StringTok{ }\KeywordTok{make.events}\NormalTok{(}
    \DataTypeTok{condition    =} \KeywordTok{trait.condition}\NormalTok{(}\DecValTok{3}\NormalTok{, }\DataTypeTok{absolute =} \OtherTok{TRUE}\NormalTok{),}
    \DataTypeTok{target       =} \StringTok{"traits"}\NormalTok{,}
    \DataTypeTok{modification =} \KeywordTok{update.traits}\NormalTok{(}\DataTypeTok{process.args =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{Sigma =} \KeywordTok{matrix}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{10}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DecValTok{2}\NormalTok{),}\DecValTok{2}\NormalTok{,}\DecValTok{2}\NormalTok{))))}

\CommentTok{## Run the simulations}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{8}\NormalTok{)}
\NormalTok{no_event <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd.params,}
                 \DataTypeTok{stop.rule =}\NormalTok{ stop.rule,}
                 \DataTypeTok{traits    =}\NormalTok{ traits)}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{8}\NormalTok{)}
\NormalTok{change_correlation <-}\StringTok{ }\KeywordTok{dads}\NormalTok{(}\DataTypeTok{bd.params =}\NormalTok{ bd.params,}
                           \DataTypeTok{stop.rule =}\NormalTok{ stop.rule,}
                           \DataTypeTok{traits    =}\NormalTok{ traits,}
                           \DataTypeTok{events    =}\NormalTok{ change_correlation)}
\CommentTok{## Visual testing}
\KeywordTok{par}\NormalTok{(}\DataTypeTok{mfrow =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{2}\NormalTok{))}
\KeywordTok{plot}\NormalTok{(no_event, }\DataTypeTok{trait =} \DecValTok{2}\NormalTok{)}
\KeywordTok{plot}\NormalTok{(change_correlation, }\DataTypeTok{trait =} \DecValTok{2}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{dads_manual_files/figure-latex/unnamed-chunk-62-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# plot(no_event, trait = c(1:2))}
\CommentTok{# plot(change_correlation, trait = c(1:2), use.3D = TRUE)}
\end{Highlighting}
\end{Shaded}

\hypertarget{event-for-changing-a-modifier}{%
\subsection{Event for changing a modifier}\label{event-for-changing-a-modifier}}
